Kindly Bent to Free Us

### 2019-07-06 kindly/lang.tex
Start working on the inference section.
Fix missing refs.

We now present the essential parts of our \lang's type system. A complete
description of the system is available in \cref{appendix:sdtyping}.
In this section, we focus on chosen parts of our system
through a set of selected rules.
%
We first define the following typing, kinding and constraint judgements:
\begin{description}
\item[$\inferS{C}{\E}{e}{\tau}$ --]
  Expression $e$ has type $\tau$ in environment $\E$ under constraints $C$.
\item[$\inferSK{C}{\E}{\tau}{k}$ --]
  Type $\tau$ has kind $k$ in environment $\E$ under constraints $C$.
\item[$\entail{D}{C}$ --] Constraint $D$ implies constraint $C$.
\end{description}

@@

\subsubsection{Environments and bindings}

\lang aims to control the usage of variables, either
through
linearity and affinity which restrict how variables are shared and ignored,
or through borrows which allow to circumvent the linearity rules
in a controlled way.
In order to check these properties, we introduce several new bindings
in our typing environments.
The grammar of type environment (noted $\E$) is shown in \cref{grammar:env}.
On top of the traditional type and value bindings, noted respectively
$\bvar{\tvar}{\kschm}$ and $\bvar{x}{\schm}$, we also consider two new
bindings.
Borrow bindings $\bvar{\borrow{x}}{\borrowty{k}{\tau}}$ indicates
that the borrow $\borrow{x}$ can be used directly, as implemented
by the rule {\sc Borrow} in \cref{selectrules:borrow}.
Suspended bindings, noted $\svar{x}{\schm}^n$, indicates that $x$
cannot be used immediately, but will be usable in a region
marked with $x$, which we detail in \cref{sdtyp:regions}.

@@

\subsubsection{Copying and Splitting}

@@

\subsubsection{Regions}
\label{sdtyp:regions}

>>>>

We now present the essential parts of our \lang's type system. A complete
description of the system is available in \cref{appendix:sdtyping}.
In this section, we focus on chosen parts of our system
through a set of selected rules.
%
We introduce the following typing, kinding and constraint judgements:
\begin{description}
\item[$\inferS{C}{\E}{e}{\tau}$ --]
  Expression $e$ has type $\tau$ in environment $\E$ under constraints $C$.
\item[$\inferSK{C}{\E}{\tau}{k}$ --]
  Type $\tau$ has kind $k$ in environment $\E$ under constraints $C$.
\item[$\entail{D}{C}$ --] Constraint $D$ implies constraint $C$.
\end{description}

@@

\subsubsection{Environments and bindings}
\label{sdtyping:envs}

\lang aims to control the usage of variables, either
through
linearity and affinity which restrict how variables are shared and ignored,
or through borrows which allow to circumvent the linearity rules
in a controlled way.
In order to check these properties, we introduce several new bindings
in our typing environments.
The grammar of type environment (noted $\E$) is shown in \cref{grammar:env}.
On top of the traditional type and value bindings, noted respectively
$\bvar{\tvar}{\kschm}$ and $\bvar{x}{\schm}$, we also consider two new
bindings.
Borrow bindings $\bvar{\borrow{x}}{\borrowty{k}{\tau}}$ indicates
that the borrow $\borrow{x}$ can be used directly, as implemented
by the rule {\sc Borrow} in \cref{selectrules:borrow}.
Suspended bindings, noted $\svar{x}{\schm}^n$, indicates that $x$
cannot be used immediately, but will be usable in a region
marked with $x$, which we detail in \cref{sdtyping:regions}.

@@

\subsubsection{Copying and Splitting}
\label{sdtyping:split}

@@

\subsubsection{Regions}
\label{sdtyping:regions}
